---
title: "Workflow"
output: html_notebook
---

### Chapter 4

R can be used as a calculator to compute basic sums. 

```{r}
5+7 
```

We can create new objects by assigning a value or a function to a name.

```{r}
x <- c(1,10)
y <- seq(1,10)
```

This object can then be called upon.

```{r}
x
y
```


#####4.4 Practice

1. Why does this code not work? 

```{r}
my_variable <- 10
my_varıable
```

The my_varıable object is not found because it is not identical to my_variable which has been assigned a value.

2. Tweaked versions of each of the R commands.

```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(mpg, model == "corvette")
```

3.
Pressing Alt+Shift+K shows all the Keyboard shortcuts that can be used to make using R easier.  
We can get to the same place by going to Help then pressing Keyboard Shortcuts Help.




### Chapter  6

The tip I used was using Ctrl+I to tidy up my script and make it look tidier. This made it easier to work with.  
Common mistakes include:  
- argument missing or extra, or missing commas.
- 
